Prediction maps of defoliation at trees

### 2019-05-22 analysis/about.Rmd
first version

---
output: github_document
---

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/pat-s/paper_hyperspectral/commits/master)  
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.5.0-brightgreen.svg)](https://cran.r-project.org/)   
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)  
<!-- [![Travis-CI Build Status](https://travis-ci.org/pat-s/paper_hyperspectral.png?branch=master)](https://travis-ci.org/pat-s/paper_hyperspectral)  -->

>>>>

---
title: "About"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

### 2019-05-22 analysis/defoliation-maps.Rmd
first version

---
title: "Prediction maps of defoliation at trees"
output: 
  html_document: 
    css: style.css
    theme: readable
    number_sections: yes
    toc: yes
    toc_float: true
    toc_collapsed: true
    df_print: tibble
    includes:
      in_header: header.html
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = "analysis/rmd/")
knitr::opts_chunk$set(
  fig.retina = 3,
  fig.align = "center",
  out.width = "100%",
  echo = FALSE
)

@@

```{r defoliation-map-2017, fig.height = 5.5, fig.width = 8.5, fig.path="../../analysis/figures/", dev = c("png")}
plot = create_defoliation_map(defoliation_raster[[1]],
                              algorithm = "XGBOOST",
                              limits = c(35, 60), title = "Defoliation of trees [%]"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-2018, fig.height = 5.5, fig.width = 8.5, fig.path="../../analysis/figures/", dev = c("png")}
plot = create_defoliation_map(defoliation_raster[[2]],
                              algorithm = "XGBOOST",
                              limits = c(35, 60), title = "Defoliation of trees [%]"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-relative-2017, fig.height = 5.5, fig.width = 8.5, fig.path="../../analysis/figures/", dev = c("png")}
plot = create_defoliation_map(defoliation_raster_relative[[1]],
                              algorithm = "XGBOOST",
                              limits = c(65, 100), title = "Relative defoliation of trees"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-relative-2018, fig.height = 5.5, fig.width = 8.5, fig.path="../../analysis/figures/", dev = c("png")}
plot = create_defoliation_map(defoliation_raster_relative[[2]],
                              algorithm = "XGBOOST",
                              limits = c(65, 100), title = "Relative defoliation of trees"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r echo = FALSE}
rmarkdown::render(here("analysis/rmd/defoliation-maps.md"), 
                  output_file = here("analysis/rmd/defoliation-maps.html"))
```

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/analysis/rmd/defoliation-maps.html -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/report-defoliation.html")
```

>>>>

---
title: "Prediction maps of defoliation at trees"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
author: "Patrick Schratz, Marc Becker, Friedrich-Schiller-University Jena"
---

```{r setup, include=FALSE}
#knitr::opts_knit$set(base.dir = "analysis/rmd/")
knitr::opts_chunk$set(
  fig.retina = 3,
  fig.align = "center",
  out.width = "100%",
  echo = FALSE
)
source(here::here("code/99-packages.R"))
sourceDirectory("R")

@@

```{r defoliation-map-2017, fig.height = 5.5, fig.width = 8.5}
plot = create_defoliation_map(defoliation_raster[[1]],
                              algorithm = "XGBOOST",
                              limits = c(35, 60), title = "Defoliation of trees [%]"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-2018, fig.height = 5.5, fig.width = 8.5}
plot = create_defoliation_map(defoliation_raster[[2]],
                              algorithm = "XGBOOST",
                              limits = c(35, 60), title = "Defoliation of trees [%]"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-relative-2017, fig.height = 5.5, fig.width = 8.5}
plot = create_defoliation_map(defoliation_raster_relative[[1]],
                              algorithm = "XGBOOST",
                              limits = c(65, 100), title = "Relative defoliation of trees"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r defoliation-map-relative-2018, fig.height = 5.5, fig.width = 8.5}
plot = create_defoliation_map(defoliation_raster_relative[[2]],
                              algorithm = "XGBOOST",
                              limits = c(65, 100), title = "Relative defoliation of trees"
)
suppressWarnings(suppressMessages(print(plot)))
```

@@

```{r echo = FALSE}
# rmarkdown::render(here("analysis/rmd/defoliation-maps.md"), 
#                   output_file = here("analysis/rmd/defoliation-maps.html"))
```

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/analysis/defoliation-maps.html -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/report-defoliation.html")
```
